### 2019-06-08 doc/chapters/trying_verify_checktx.tex
more text

This chapter describes the part of Bitcoin-S needed to verify the No Inflation Property described before.
We are going to create a transaction and show you the relevant parts of the method checkTransaction, where transactions are checked against some properties.
Then we see some troubles occurred during this work.
In the end you will see how we fixed a bug in Bitcoin-S.

@@

\section{Adjusting Property}

Trying to integrate Stainless in Bitcoin-S caused a lot of troubles, because of version conflicts.
If you are interested in it you can read more in the appendix \ref{chap:appendix_arb}.

>>>>

This chapter describes the part of Bitcoin-S needed to verify the No Inflation Property described before.
We are going to create a transaction and show you the relevant parts of the method checkTransaction, where transactions are checked against some properties.
Then, we will see the bug in Bitcoin-S found during this work and its fix.
In the end we find reasons why it was needed for this work to change the verification from the No Inflation Property to the Addition with Zero Property.

@@

\section{Adjusting No Inflation Property}

Trying to integrate Stainless in Bitcoin-S caused a lot of troubles, mainly because of version conflicts.
You can find more about it in chapter \ref{chap:appendix_arb}.
